### 2020-01-30 ChapterConclusion/chapterConclusion.tex
Updated: Summary of chapters to Conclusion. More Further Work

\chapter{Conclusions and Future Work}
An approach to networked real-time physics simulations that is scalable and alleviates the processing limitation of a single server has been presented. Only open-source software has been used in our approach and our algorithm has been developed in a way that is agnostic to any specific application technology.

@@

We have measured and evaluated the correctness of collisions in AP. Our experiments establish that collisions remain correct in AP, even when objects interact while intersecting the boundary. This has been shown to be true while increasing each of the following factors: speed; latency and frame-time. Collisions remain correct up to the tolerance values for each factor and begin to show errors as soon as the tolerance is exceeded, demonstrating the correctness of the aura calculation used in AP. In addition the effects of packet loss on the system have also been explored and the limits of AP with increasing packet loss have been shown. This paper demonstrates that collisions of rigid-bodies can be handled correctly in a scalable, distributed real-time physics system, even when those collisions take place on or near a server-region boundary.

%Thrashing, if we do it?

Our continuing work will be to carry out experiments to determine the effects that changing each of the aura tolerances has on the performance and scalability of AP. Future work will enable each tolerance value to be dynamic and the aura size could adapt with the changing conditions of the system. This would improve performance when factors are low and maintain correctness when factors are high.

@@

We will also be researching the use of modern cloud technologies such as containers and container orchestration in order to facilitate efficient provisioning and management of additional compute resources within a distributed physics simulation. The use of lightweight containers versus virtual machine instances may allow for more precise control of compute resource allocation and faster on-demand provisioning, which would lend itself well to streamed gaming applications.

@@

>>>>

\chapter{Conclusions and Future Work}
\section{Conclusions}
An approach to networked real-time physics simulations that is scalable and alleviates the processing limitation of a single server has been presented. Only open-source software has been used in our approach and our algorithm has been developed in a way that is agnostic to any specific application technology.

In Chapter \ref{ProbDef} the challenges facing distributed real-time physics were defined, possible solutions were addressed and our chosen solution, AP, was presented and justified. The origination of the aura calculation used for the auras in AP was also presented. The implementation of AP was discussed in Chapter \ref{Implementation}, including potential topologies that could be used by a system using AP and the breakdown of the components of each server. Chapter \ref{Implementation} also gave an overview of the visualiser used by the system, which is responsible for rendering the state of the simulation through the use of replicas. Its features and their implementation details were discussed.

In Chapter \ref{Results}, the design and results of the experiments were presented for addressing the questions set out by this study: "Can scalable real-time physics simulations be achieved?" and "Can real-time physics simulations remain correct when scaled?".

@@

We have measured and evaluated the correctness of collisions in AP. Our experiments establish that collisions remain correct in AP, even when objects interact while intersecting the boundary. This has been shown to be true while increasing each of the following factors: speed; latency and frame-time. Collisions remain correct up to the tolerance values for each factor and begin to show errors as soon as the tolerance is exceeded, demonstrating the correctness of the aura calculation used in AP. The holds true if thrashing collisions are excluded from the results. The number of thrashing collisions and amount of times thrashed were both measured, potential solutions to the thrashing problem were proposed in \ref{Thrashing} and we assume that these errors will be fixed in future work.

In addition to the aura factors being tested, the effects of packet loss on the system have also been explored and the limits of AP with increasing packet loss have been shown. This paper demonstrates that collisions of rigid-bodies can be handled correctly in a scalable, distributed real-time physics system, even when those collisions take place on or near a server-region boundary.

\section{Future Work}
Our continuing work will be to carry out experiments to determine the effects that changing each of the aura tolerances has on the performance and scalability of AP. Future work will enable each tolerance value to be dynamic and the aura size could adapt with the changing conditions of the system. This would improve performance when factors are low and maintain correctness when factors are high.

Acceleration could also be factored into the aura calculation. The velocity between time steps is often limited and using an acceleration tolerance would allow for smaller auras for slow moving objects. Smaller auras lead to better performance as it leads to fewer aura broadcasts and object migrations. Note that the acceleration tolerance could only apply to the displacement calculation of the local object, as the velocity of a potential remote object is unknown.
%Reference where smaller auras improving performance are explained

An alternative to just aura position and radius being sent, more details of the object could be sent, including bounding sphere and velocity. This would allow the receiving server to determine the size of the aura. Under changing conditions, such as changes in latency the receiving server could dynamically change the size of the auras without the need for the sending server to send the new sizes of the auras.

@@

The use of modern cloud technologies will also be researched, such as containers and container orchestration in order to facilitate efficient provisioning and management of additional compute resources within a distributed physics simulation. The use of lightweight containers versus virtual machine instances may allow for more precise control of compute resource allocation and faster on-demand provisioning, which would lend itself well to streamed gaming applications.

Future cloud deployment architectures could also be investigated. The use of `overseer' nodes to enable scalability in terms of clients connected could be developed and measured, and their ability to provide a level of fault-tolerance in the event of node failure could be tested. Overseer nodes could also be located at the edge, providing lower latencies for connecting clients, but at the cost of a higher latency between overseer nodes and the cloud-based simulation servers and the other overseer nodes.

%Render nodes
%Edge computing

@@

%Constraints
AP is currently limited to the migration of single rigid-bodies between servers. Support for other physical entities such as groups of attached rigid-bodies, soft-bodies and constraints within AP could be added and investigated.

### 2020-01-30 ChapterProblemDefinition/chapterProblemDefinition.tex
Updated: Label for Corner Case in Problem Definition
Updated: Summary of chapters to Conclusion. More Further Work

\chapter{Problem Definition and Proposed Solution}
%	\item Naive approach. How would a naive approach behave and what problems occur.
%\item Considered Solutions. We consider a number of solutions to scalable real-time physics.
%\item Proposed Solution. We look at in more detail how our solution works and justification for its choice.
%\item Aura Calculation. A detailed look at the important aspect of AP, the aura calculation.
%\item Sub-optimal object hosting. We look at one the predicted challenge with AP, sub-optimal object hosting and discuss a solution which can be addressed in future work.
%\item Thrashing. A further predicted challenge with AP, this consists of two types of thrashing, two and three object thrashing, three object thrashing has been solved in this implementation of AP and we discuss solutions to two object thrashing.
%\item Islands. A solved challenge with AP, here we discuss our solution.
%\item Corner Case. AP has been discussed in terms of a single boundary between two servers up to this point, but in order for a general solution to be achieved, AP must be able to support boundaries between three or more servers, such as at corners.

@@

\section{Corner Case}
This section discusses how AP handles corner cases, i.e., where the boundary of more than two servers meet.

>>>>

\chapter{Problem Definition and Proposed Solution}\label{ProbDef}
%	\item Naive approach. How would a naive approach behave and what problems occur.
%\item Considered Solutions. We consider a number of solutions to scalable real-time physics.
%\item Proposed Solution. We look at in more detail how our solution works and justification for its choice.
%\item Aura Calculation. A detailed look at the important aspect of AP, the aura calculation.
%\item Sub-optimal object hosting. We look at one the predicted challenge with AP, sub-optimal object hosting and discuss a solution which can be addressed in future work.
%\item Thrashing. A further predicted challenge with AP, this consists of two types of thrashing, two and three object thrashing, three object thrashing has been solved in this implementation of AP and we discuss solutions to two object thrashing.
%\item Islands. A solved challenge with AP, here we discuss our solution.
%\item Corner Case. AP has been discussed in terms of a single boundary between two servers up to this point, but in order for a general solution to be achieved, AP must be able to support boundaries between three or more servers, such as at corners.

@@

\section{Corner Case}\label{CornerCase}
This section discusses how AP handles corner cases, i.e., where the boundary of more than two servers meet.

### 2020-01-30 ChapterResults/chapterResults.tex
Updated: Summary of chapters to Conclusion. More Further Work

\chapter{Experiments and Results}
In this chapter, experiments for testing both the scalability and correctness of AP are designed and justified, the results of which, are analysed and evaluated. Scalability experiments are carried out with increasing numbers of servers in both column and corner topologies. Correctness experiments are carried out using two servers and two objects, one from each server, colliding with each other under different conditions and with different tolerances used for the aura calculation.

>>>>

\chapter{Experiments and Results}\label{Results}
In this chapter, experiments for testing both the scalability and correctness of AP are designed and justified, the results of which, are analysed and evaluated. Scalability experiments are carried out with increasing numbers of servers in both column and corner topologies. Correctness experiments are carried out using two servers and two objects, one from each server, colliding with each other under different conditions and with different tolerances used for the aura calculation.
